---
title: "Average's calculation of the1st semester of master 2 probability and statistics."
author: "Cylia YACEF"
date: '2022-08-13'
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## About the Course Project

This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github


## How to use the application
This application allows students of Master 2 majoring in probability and statistics to calculate their first semester's average.

ui.R, and Server.R Code in my github repository

https://github.com/cylia2131/Shiny-Application-and-Reproducible-Pitch

## Run the application

The application is available at 

https://415p7a-cylia-yacef.shinyapps.io/mean/?_ga=2.38167843.1046915759.1660402315-2031391207.1660402315

All you have to do is enter your exams marks.

##
The app appears like this

```{r eruptions }

library(shiny) 
shinyUI(
  pageWithSidebar(
    # Application title
    headerPanel("Average's calculation of the1st semester of master 2 probability and statistics."),
    
    sidebarPanel(
      numericInput('Regression_model', 'Insert your Regression model mark', 10,min = 0, max = 20, step = 0.5) ,
      numericInput('Waiting_system', 'Insert your Waiting system mark', 10, min = 0, max = 20, step = 0.5) ,
      numericInput('Time_series', 'Insert your Time series mark',10, min = 0, max = 20, step = 0.5) ,
      numericInput('Extreme_value_theory', 'Insert your Extreme value theory mark',10, min = 0, max = 20, step = 0.5) ,
      numericInput('Martingale_theory', 'Insert your Martingale theory mark',10, min = 0, max = 20, step = 0.5) ,
      numericInput('Monte_Carlo_method', 'Insert your Monte Carlo method mark',10, min = 0, max = 20, step = 0.5) ,
      numericInput('Tic_and_Management', 'Insert your Tic and Management mark',10, min = 0, max = 20, step = 0.5) ,
      numericInput('Educational_engineering', 'Insert your Educational engineering mark',10, min = 0, max = 20, step = 0.5) 
    ), 
    mainPanel(
      h3('This application calculates the average of the first semester'),
      h3('Pass or fail is evaluated as follows:'),
      h3(tags$div(
        tags$ul(
          tags$li('Average <10,       : Failed'),
          tags$li('Average >= 10 : Passed')
        )
      )),
      
      h3(), 
      verbatimTextOutput("inputRegression_modelmark"),
      verbatimTextOutput("inputWaiting_systemmark"),
      verbatimTextOutput("inputTime_seriesmark"),
      verbatimTextOutput("inputExtreme_value_theorysmark"),
      verbatimTextOutput("inputMartingale_theorymark"),
      verbatimTextOutput("inputMonte_Carlo_methodmark"),
      verbatimTextOutput("inputTic_and_Managementmark"),
      verbatimTextOutput("inputEducational_engineeringmark"),
      
      h3('Your calulated AVERAGE RESULT is:'),
      verbatimTextOutput("estimation"),
      h3('It means that you:'),strong(verbatimTextOutput("diagnostic"))
      
    )
    
  )   
)



shinyServer(
  function(input, output) {
Average_Factor<-function(Regression_model,Waiting_system,Time_series,
                         Extreme_value_theory, Martingale_theory,
                         Monte_Carlo_method, Tic_and_Management,
                         Educational_engineering) {(Regression_model*2 +                              Waiting_system*3 +Time_series*2         +Extreme_value_theory*2 + Martingale_theory *3 + Monte_Carlo_method*2+ Tic_and_Management + Educational_engineering)/17}

diagnostic_f<-function(Regression_model,Waiting_system,Time_series,
                       Extreme_value_theory, Martingale_theory,
                       Monte_Carlo_method, Tic_and_Management,
                       Educational_engineering){
  
  Average_value<-(Regression_model*2 + Waiting_system*3 +
                    Time_series*2 + Extreme_value_theory*2 +
                    Martingale_theory *3 + Monte_Carlo_method*2+
                    Tic_and_Management + Educational_engineering)/17
  
  if(Average_value < 10) return("Failed")
  else 
    if(Average_value >=10) return ("Passed")
  }


    
      output$estimation <- renderPrint({Average_Factor(input$Regression_model,input$Waiting_system, input$Time_series,input$Extreme_value_theory,input$Martingale_theory, input$Monte_Carlo_method, input$Tic_and_Management, input$Educational_engineering)})
   
       output$diagnostic <- renderPrint({diagnostic_f(input$Regression_model,input$Waiting_system, input$Time_series,input$Extreme_value_theory, input$Martingale_theory,input$Monte_Carlo_method, input$Tic_and_Management, input$Educational_engineering)})
  } 
) 


```
